### 2025-06-18 simulation.qmd
20250618 - fix
20250618 - citations

```{r}
#| label: code-to-specify-vars-to-bootstrap-by-position
#| eval: false

@@

@@

rm(bootstrappedFantasyPoints)
gc()
```

@@

You can generate a template for Monte Carlo simulations in the `SimDesign` package using the following code:

>>>>

@@

For performing the bootstrapping, we leverage the `data.table` [@R-data.table], `future` [@R-future], and `future.apply` [@R-future.apply] packages for speed (by using parallel processing) and memory efficiency.
We use the `progressr` [@R-progressr] package to create a progress bar.

@@

@@

You can generate a template for Monte Carlo simulations in the `SimDesign` [@R-SimDesign; @Chalmers2020] package using the following code:
